Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-11 thirdPaper/draft/typeConeAssociahedra.tex
schema
Remark 1.6 changed to a Definition

% Schematic diagram:
\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
\arnau{As tu une idée en tête de comment le répresenter? Je trouve que ce que t'as écrit est très clair et je ne vois pas comment faire une schema qui le ameillore}
% 
% I.1 explains the type cone approach to the problem
% 
% This strategy is used in I.2.2 for cluster algebras and in I.2.3 for gentle algebras.
% 
% II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2 for proving U.E.R.P. and simpliciality of the type cone.
% 
% II.4 generalises II.3, is used in I.2.3 for proving the U.E.R.P. and offers a different proof of simpliciality of the type cone .

@@

\begin{remark}
\label{rem:dimTypeCone}
Since the type cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).
We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
\end{remark}

>>>>

\noindent {\bf Schematic diagram of logical dependencies:}

\begin{center}
\includegraphics[scale=.9]{Schema}
\end{center}

% Schematic diagram:
% \yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
% \arnau{As tu une idée en tête de comment le répresenter? Je trouve que ce que t'as écrit est très clair et je ne vois pas comment faire une schema qui le ameillore}
% 
% I.1 explains the type cone approach to the problem
% 
% This strategy is used in I.2.2 for cluster algebras and in I.2.3 for gentle algebras.
% 
% II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2 for proving U.E.R.P. and simpliciality of the type cone.
% 
% II.4 generalises II.3, is used in I.2.3 for proving the U.E.R.P. and offers a different proof of simpliciality of the type cone .

@@

Since the type cone is an~$N$-dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).

\begin{definition}
\label{rem:dimTypeCone}
The type cone is \defn{simplicial} when it has precisely $N-n$ facets.
\end{definition}
